A Dearth of Young Stars and Planets in the Kepler Field

### 2024-06-03 paper/ms.tex
update ms

\subsubsection{Comparing Rotation and Lithium Ages}

The comment column of Table~\ref{tab:planets} compares
the independent rotation and lithium ages of the
known planet hosts using the point-estimates of their age posteriors.
There are three cases of interest.
{\it 1i)} If two-sided posteriors for both $t_{\rm gyro}$ and $t_{\rm Li}$ existed,
and their values were consistent within 2$\sigma$, we judged them
to be consistent; if they were consistent within 2-3$\sigma$, we
listed them as ``maybe'' consistent.  Otherwise, they
disagreed.
{\it ii)}
If $t_{\rm Li}$ was a lower limit, we compared this lower limit
with the $1\sigma$ upper limit from $t_{\rm gyro}$; if the two
overlapped, we judged the age estimates to be consistent.
{\it iii)}
If $t_{\rm Li}$ provided a two-sided posterior, and no
rotation period was found, we judged the age estimates to be
inconsistent.  This is because a two-sided lithium constraint can only be
provided for G and K stars $\lesssim$2\,Gyr old, and Kepler should
have been sensitive to the rotation periods of such stars.

@@

Let us restrict discussion to blemish-free stars with 
confirmed planets: $Q_{\rm star}$ must not have any of bits zero
through nine raised, and $Q_{\rm planet}$ must also have no quality flags
raised.  Under this constraint, our results include
\ltonegyrhighqconfirmedtwosided\ systems younger than 1\,Gyr with
two-sided $t_{\rm gyro}$ and $t_{\rm Li}$, and
\ltonegyrhighqconfirmedonesided\ cases for which $t_{\rm gyro}$
provides an age constraint while $t_{\rm Li}$ is one-sided.

>>>>

\subsubsection{Rotation vs.~Lithium Ages}

We compared 
the rotation and lithium ages for the
known planet hosts 
in the ``comment'' column of Table~\ref{tab:planets}.
There were three cases of interest.
{\it i)} If two-sided posteriors for both $t_{\rm gyro}$ and $t_{\rm Li}$ existed,
and their median values were consistent within 2$\sigma$, we listed them
as consistent; if they were consistent within 2-3$\sigma$, we
listed them as ``maybe'' consistent.  Otherwise, they
disagreed.
{\it ii)}
If $t_{\rm Li}$ was a lower limit, we compared this lower limit
with the $1\sigma$ upper limit from $t_{\rm gyro}$; if the two
overlapped, we judged the age estimates to be consistent.
{\it iii)}
If $t_{\rm Li}$ provided a two-sided posterior, and no
rotation period was found, we judged the age estimates to be
inconsistent.  This is because a two-sided lithium constraint can only be
provided for G and K dwarfs $\lesssim$2\,Gyr old, and Kepler should
have been sensitive to the rotation periods of such stars.

@@

Let us focus discussion on blemish-free stars with 
confirmed planets: $Q_{\rm star}$ must not have any of bits zero
through nine raised, and $Q_{\rm planet}$ must also have no quality flags
raised.  Under this constraint, our results include
\ltonegyrhighqconfirmedtwosided\ systems younger than 1\,Gyr with
two-sided $t_{\rm gyro}$ and $t_{\rm Li}$, and
\ltonegyrhighqconfirmedonesided\ cases for which $t_{\rm gyro}$
provides an age constraint while $t_{\rm Li}$ is one-sided.
